---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
```

```{css}
body {
  font-family: "Times New Roman", serif;
  line-height: 1.6;
}

h2 {
  color: #D8A;
}

p {
  font-size: 16px;
}
```

```{r}
csv_file <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vT3UNIsOjEigNCiSvkmsavvAPOu7guGHh5HL1QxQwXUo8-qx8nPHAphl0w3fXcETSdHVdBD_CnGNB-d/pub?gid=1703901117&single=true&output=csv"

logged_data <- read_csv(csv_file)

latest_data <- logged_data %>%
  rename(
    time = `What time is this observation?`,
    purpose = `What is the main purpose of phone use?`,
    duration = `How long did you use your phone?`,
    battery = `What was your phone battery level at the start of this usage?`,
    location = `Where are you?`,
    multitask = `Were you doing something else at the same time while using your phone?`
  ) %>%
  mutate(
    duration = as.numeric(duration),
    battery = as.numeric(battery),
    time = factor(
      time
      )
    )
```

## Phone usage patterns throughout the day

This report explores data collected on phone usage throughout the day. It looks at when people use their phones, where they are when using them, and some basic summary patterns in the dataset.


```{r}
# Mean phone usage duration
mean_duration <- mean(latest_data$duration, na.rm = TRUE)

# Maximum phone usage duration
max_duration <- max(latest_data$duration, na.rm = TRUE)
 
# Most common time of day for phone usage
most_common_time <- latest_data %>%
  count(time, sort = TRUE) %>%
  slice(1) %>%
  pull(time)

```

- The average phone usage duration recorded in this dataset is **`r mean_duration`** minutes. 

- The longest phone usage recorded is **`r max_duration`** minutes. 

- The most common time of day for phone usage in this dataset is **`r most_common_time`**. 

```{r}

# Bar chart: Time of day
latest_data %>%
  ggplot(aes(x = time)) +
    geom_bar(fill = "#B5EAD7") +
  labs(title = "Phone Usage by Time of Day", 
       x = "Time",
       y = "Count"
       ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 30, hjust = 1)
  )

```

This bar chart shows how phone usage observations are distributed across different times of the day. 

```{r}

# Bar chart: Time of Day by Location of Phone Usage
latest_data %>%
  ggplot() +
  geom_bar(aes(x = time, fill = location)) +
  labs(
    title = "Phone Usage by Time of Day and Location",
    x = "Time of Day",
    y = "Count",
    fill = "Location"
  ) +
  scale_fill_manual(values = c(
    "#FFC5D3",
    "#A8DADC",
    "#FFE5B4",
    "#CDB4DB",
    "#B5EAD7"
  )) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 30, hjust = 1)
  )

```

This bar chart shows the relationship between time of day and location of phone usage. It helps show where respondents are most likely to be when using their phones at different times. 